Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-23 workflow/workflow.Rmd
Start addressing Sandrine points

```{r parallel}
NCORES <- 2
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing on your computer.")
  register(SerialParam())
}
```

@@

There are three special sets of genes in this dataset: the CreER gene corresponds to the estrogen receptor fused to Cre recombinase (Cre-ER), which is used to activate HBCs into differentiation following injection of tamoxifen (see [@Fletcher2017] for details); [*** SD: Do you mean the "Sox2-eGFP gene"?] the Sox2-eGFP transgenic was used for FACS sorting; the ERCC spike-in sequences are synthetic genes spiked-in at known concentrations and used for quality control purposes.

@@

To compute the gene-wise variances and keep only the most variable genes, we use two functions from the `clusterExperiment` package. In particular, `makeFilterStats` will compute the variance of the gene expression data with a given transformation applied to the counts (in this case `log(x+1)`) and store the variance values in the `rowData` slot of the object [*** SD: Which object?]. `filterData` will then use the computed values to keep only the desired number of genes.

>>>>

```{r parallel}
NCORES <- 6
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing on your computer.")
  register(SerialParam())
}
```

@@

There are three special sets of genes in this dataset: the CreER gene corresponds to the estrogen receptor fused to Cre recombinase (Cre-ER), which is used to activate HBCs into differentiation following injection of tamoxifen (see [@Fletcher2017] for details); the Sox2-eGFP transgene was used for FACS sorting; the ERCC spike-in sequences are synthetic genes spiked-in at known concentrations and used for quality control purposes.

@@

To compute the gene-wise variances and keep only the most variable genes, we use two functions from the `clusterExperiment` package. In particular, `makeFilterStats` will compute the variance of the gene expression data with a given transformation applied to the counts (in this case `log(x+1)`) and store the variance values in the `rowData` slot of the resulting `SingleCellExperiment` object. `filterData` will then use the computed values to keep only the desired number of genes.
